### 2016-06-13 README.Rmd
Initial commit

---
title: "{mscstexta4r}"
subtitle: "R Client for the Microsoft Cognitive Services Text Analytics REST API"
author: "Phil Ferriere"
date: "June 2016"
geometry: margin=0cm
output:
  html_document:
    self_contained: true
    highlight: tango
    keep_md: yes
    theme: cerulean
    toc: yes
    toc_depth: 4
    toc_float: yes
---
```{r echo=FALSE}
library("knitr")
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```
[![Build Status](https://api.travis-ci.org/philferriere/mscstexta4r.png)](https://travis-ci.org/philferriere/mscstexta4r)
[![codecov.io](https://codecov.io/github/philferriere/mscstexta4r/coverage.svg?branch=master)](https://codecov.io/github/philferriere/mscstexta4r?branch=master)
[![CRAN Version](http://www.r-pkg.org/badges/version/mscstexta4r)](https://cran.r-project.org/package=mscstexta4r)

[Microsoft Cognitive Services](https://www.microsoft.com/cognitive-services/en-us/documentation)
-- formerly known as Project Oxford -- are a set of APIs, SDKs and services
that developers can use to add [AI](https://en.wikipedia.org/wiki/Artificial_intelligence)
features to their apps. Those features include emotion and video detection;
facial, speech and vision recognition; and speech and natural language
processing ([NLP](https://en.wikipedia.org/wiki/Natural_language_processing)).

> Note: A test/demo Shiny web application is available [here](https://github.com/philferriere/mscsshiny).

## What's the Text Analytics REST API?

Per Microsoft's website, the [Text Analytics REST API](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation)
is a suite of text analytics web services built with Azure Machine Learning that
can be used to analyze unstructured text. The API supports four text analysis
operations:

* Sentiment analysis - Is a sentence or document generally positive or negative?
* Topic detection - What's being discussed across a list of documents/reviews/articles?
* Language detection - What language is a document written in?
* Key talking points extraction - What's being discussed in a single document?

### Sentiment analysis

The API returns a numeric score between 0 and 1. Scores close to 1 indicate
positive sentiment and scores close to 0 indicate negative sentiment. Sentiment
score is generated using classification techniques. The input features of the
classifier include n-grams, features generated from part-of-speech tags, and
word embeddings. English, French, Spanish and Portuguese text are supported.

### Topic detection

This API returns the detected topics for a list of submitted text records. A
topic is identified with a key phrase, which can be one or more related words.
This API requires a minimum of 100 text records to be submitted, but is designed
to detect topics across hundreds to thousands of records. The API is designed to
work well for short, human-written text such as reviews and user feedback.

### Language detection

This API returns the detected language and a numeric score between 0 and 1.
Scores close to 1 indicate 100% certainty that the identified language is
correct. A total of 120 languages are supported.

### Extraction of key talking points

This API returns a list of strings denoting the key talking points in the input
text. English, German, Spanish, and Japanese text are supported.

To use the `{mscstexta4r}` R package, you **MUST** have a valid [account](https://www.microsoft.com/cognitive-services/en-us/pricing)
with Microsoft Cognitive Services. Once you have an account, Microsoft will
provide you with an [API key](https://en.wikipedia.org/wiki/Application_programming_interface_key).
This key will be listed under your subscriptions.

After you've configured `{mscstexta4r}` with your API key, you will be able to
call the Text Analytics REST API from R, up to your maximum number of
transactions per month and per minute.

## Package Installation

You can either install the latest **stable** version from CRAN:

```{r eval=FALSE}
if ("mscstexta4r" %in% installed.packages()[,"Package"] == FALSE) {
  install.packages("mscstexta4r")
}
```

Or, you can install the **development** version

```{r eval=FALSE}
if ("mscstexta4r" %in% installed.packages()[,"Package"] == FALSE) {
  if ("devtools" %in% installed.packages()[,"Package"] == FALSE) {
    install.packages("devtools")
  }
  devtools::install_github("philferriere/mscstexta4r")
}
```

## Package Loading and Configuration

After loading `{mscstexta4r}` with `library()`, you **must** call `textaInit()`
before you can call any of the core `{mscstexta4r}` functions.

The `textaInit()` configuration function will first check to see if the variable
`MSCS_TEXTANALYTICS_CONFIG_FILE` exists in the system environment. If it does,
the package will use that as the path to the configuration file.

If `MSCS_TEXTANALYTICS_CONFIG_FILE` doesn't exist, it will look for the file
`.mscskeys.json` in the current user's home directory (that's `~/.mscskeys.json`
on Linux, and something like `C:\Users\Phil\Documents\.mscskeys.json` on
Windows). If the file is found, the package will load the API key and URL from
it.

If using a file, please make sure it has the following structure:

```json
{
  "textanalyticsurl": "https://westus.api.cognitive.microsoft.com/texta/analytics/v2.0/",
  "textanalyticskey": "...MSCS Text Analytics API key goes here..."
}
```

If no configuration file is found, `textaInit()` will attempt to pick up its
configuration from two Sys env variables instead:

`MSCS_TEXTANALYTICS_URL` - the URL for the Text Analytics REST API.

`MSCS_TEXTANALYTICS_KEY` - your personal Text Analytics REST API key.

`textaInit()` needs to be called *only once*, after package load.

## Error Handling

The MSCS Text Analytics API is a **[RESTful](https://en.wikipedia.org/wiki/Representational_state_transfer)** API.
HTTP requests over a network and the Internet can fail. Because of congestion,
because the web site is down for maintenance, because of firewall configuration
issues, etc. There are many possible points of failure.

The API can also fail if you've **exhausted your call volume quota** or are
**exceeding the API calls rate limit**. Unfortunately, MSCS does not expose an
API you can query to check if you're about to exceed your quota for instance.
The only way you'll know for sure is by **looking at the error code** returned
after an API call has failed.

To help with error handling, we recommend the systematic use of `tryCatch()`
when calling `{mscstexta4r}` core functions. Its mechanism may appear a bit
daunting at first, but it is well [documented](http://www.inside-r.org/r-doc/base/signalCondition).
We've also included many examples, as you'll see below.

## Synchronous vs Asynchronous Execution

All but **one** core text analytics functions execute exclusively in synchronous
mode. `textaDetectTopics()` is the only function that can be executed either
synchronously or asynchronously. Why? Because topic detection is typically a
"batch" operation meant to be performed on thousands of related documents
(product reviews, research articles, etc.).

### What's the Difference?

When `textaDetectTopics()` executes synchronously, you must wait for it to
finish before you can move on to the next task. When `textaDetectTopics()`
executes asynchronously, you can move on to something else before topic
detection has completed. In the latter case, you will need to call
`textaDetectTopicsStatus()` periodically yourself until the Microsoft Cognitive
Services server complete topic detection and results become available.

### When to Run Which Mode

If you're performing topic detection in batch mode (from an R script), we
recommend using the `textaDetectTopics()` in synchronous mode, in which case,
again, it will return only after topic detection has completed.

If you're calling `textaDetectTopics()` in synchronous mode within the R console
REPL (interactive mode), it will **appear as if the console has hanged**. This
is *EXPECTED*. The function hasn't crashed. It is simply in "sleep mode",
activating itself periodically and then going back to sleep, until the results
have become available. In sleep mode, even though it appears "stuck",
`textaDetectTopics()` doesn't use any CPU resources. While the function is
operating in sleep mode, you *WILL NOT* be able to use the console before the
function completes. If you need to operate the console while topic detection is
being performed by the Microsoft Cognitive services servers, you should call
`textaDetectTopics()` in asynchronous mode and then call
`textaDetectTopicsStatus()` yourself repeatedly afterwards, until results are
available.

## Package Configuration with Error Handling

Here's some sample code that illustrates how to use `tryCatch()`:

```{r}
library('mscstexta4r')
tryCatch({

  textaInit()

}, error = function(err) {

  geterrmessage()

})
```

If `{mscstexta4r}` cannot locate `.mscskeys.json` nor any of the configuration
environment variables, the code above will generate the following output:

```{r eval=FALSE}
[1] "mscstexta4r: could not load config info from Sys env nor from file"
```

Similarly, `textaInit()` will fail if `{mscstexta4r}` cannot find the
`textanalyticskey` key in `.mscskeys.json`, or fails to parse it correctly,
etc. This is why it is so important to use `tryCatch()` with all `{mscstexta4r}`
functions.

## Package API

The core API calls exposed by `{mscstexta4r}` are the following:

```{r eval = FALSE}
# Perform sentiment analysis
textaSentiment(
  documents,                  # Input sentences or documents
  languages = rep("en", length(documents))
  # "en"(English, default)|"es"(Spanish)|"fr"(French)|"pt"(Portuguese)
)
```

```{r eval = FALSE}
# Detect top topics in group of documents
textaDetectTopics(
  documents,                  # At least 100 documents
  stopWords = NULL,           # Stop word list (optional)
  topicsToExclude = NULL,     # Topics to exclude (optional)
  minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
  maxDocumentsPerWord = NULL, # Threshold to exclude ubiquitous topics (optional)
  resultsPollInterval = 30L,  # Poll interval (in s, default: 30s, use 0L for async)
  resultsTimeout = 1200L,     # Give up timeout (in s, default: 1200s = 20mn)
  verbose = FALSE             # If set to TRUE, print every poll status to stdout
)
```

```{r eval = FALSE}
# Detect languages used in documents
textaDetectLanguages(
  documents,                      # Input sentences or documents
  numberOfLanguagesToDetect = 1L  # Default: 1L
)
```

```{r eval = FALSE}
  # Get key talking points in documents
textaKeyPhrases(
  documents,                  # Input sentences or documents
  languages = rep("en", length(documents))
  # "en"(English, default)|"de"(German)|"es"(Spanish)|"fr"(French)|"ja"(Japanese)
)
```

The functions `textaDetectTopics()` returns a S3 class object of the class
`textatopics`. The `textatopics` object exposes formatted results using several
dataframes (documents and their IDs, topics and their IDs, which topics are
assigned to which documents), the REST API JSON response (should you care),
and the HTTP request (mostly for debugging purposes).

The other functions return S3 class objects of the class `texta`. The `texta`
object exposes results collected in a single `data.frame`, the REST API JSON
response, and the original HTTP request.

## Sample Code

The following code snippets illustrate how to use {mscstexta4r} functions and
show what results they return with toy examples. If after reviewing this code
there is still confusion regarding how and when to use each function, please
refer to the [original documentation](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation).

### Sentiment Analysis

```{r}
docsText <- c(
  "Loved the food, service and atmosphere! We'll definitely be back.",
  "Very good food, reasonable prices, excellent service.",
  "It was a great restaurant.",
  "If steak is what you want, this is the place.",
  "The atmosphere is pretty bad but the food is quite good.",
  "The food is quite good but the atmosphere is pretty bad.",
  "The food wasn't very good.",
  "I'm not sure I would come back to this restaurant.",
  "While the food was good the service was a disappointment.",
  "I was very disappointed with both the service and my entree."
)
docsLanguage <- rep("en", length(docsText))

tryCatch({

  # Perform sentiment analysis
  textaSentiment(
    documents = docsText,    # Input sentences or documents
    languages = docsLanguage
    # "en"(English, default)|"es"(Spanish)|"fr"(French)|"pt"(Portuguese)
)

}, error = function(err) {

  # Print error
  geterrmessage()

})
```

### Topic Detection (synchronous mode)

```{r}
# Load yelpChReviews100 text reviews
load("./tests/testthat/data/yelpChineseRestaurantReviews100.rda")

tryCatch({

  # Detect top topics
  textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences
    stopWords = NULL,             # Stop word list (optional)
    topicsToExclude = NULL,       # Topics to exclude (optional)
    minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
    maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
    resultsPollInterval = 30L,    # Poll interval (in s, default: 30s, use 0L for async)
    resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
    verbose = FALSE               # If set to TRUE, print every poll status to stdout
  )

}, error = function(err) {

  # Print error
  geterrmessage()

})
```

### Topic Detection (asynchronous mode)

```{r}
# Load yelpChReviews100 text reviews
load("./tests/testthat/data/yelpChineseRestaurantReviews100.rda")

tryCatch({

  # Detect top topics
  operation <- textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences
    resultsPollInterval = 0L      # Poll interval (in s, default: 30s, use 0L for async)
  )

  # Poll the servers ourselves, until the work completes or until we time out
  resultsPollInterval <- 30L
  resultsTimeout <- 1200L
  startTime <- Sys.time()
  endTime <- startTime + resultsTimeout

  while (Sys.time() <= endTime) {
    sleepTime <- startTime + resultsPollInterval - Sys.time()
    if (sleepTime > 0)
      Sys.sleep(sleepTime)
    startTime <- Sys.time()

    # Poll for results
    topics <- textaDetectTopicsStatus(operation)
    if (topics$status != "NotStarted" && topics$status != "Running")
      break;
  }

  topics

}, error = function(err) {

  # Print error
  geterrmessage()

})
```

### Language Detection

```{r}
docsText = c(
  "The Louvre or the Louvre Museum is the world's largest museum.",
  "Le musée du Louvre est un musée d'art et d'antiquités situé au centre de Paris.",
  "El Museo del Louvre es el museo nacional de Francia.",
  "Il Museo del Louvre a Parigi, in Francia, è uno dei più celebri musei del mondo.",
  "Der Louvre ist ein Museum in Paris."
)

tryCatch({

  # Detect languages
  textaDetectLanguages(
    documents = docsText,           # Input sentences or documents
    numberOfLanguagesToDetect = 1L  # Number of languages to detect
  )

}, error = function(err) {

  # Print error
  geterrmessage()

})
```

### Key Talking Points Extraction

```{r}
docsText <- c(
  "Loved the food, service and atmosphere! We'll definitely be back.",
  "Very good food, reasonable prices, excellent service.",
  "It was a great restaurant.",
  "If steak is what you want, this is the place.",
  "The atmosphere is pretty bad but the food is quite good.",
  "The food is quite good but the atmosphere is pretty bad.",
  "I'm not sure I would come back to this restaurant.",
  "The food wasn't very good.",
  "While the food was good the service was a disappointment.",
  "I was very disappointed with both the service and my entree."
)
docsLanguage <- rep("en", length(docsText))

tryCatch({

  # Get key talking points in documents
  textaKeyPhrases(
    documents = docsText,    # Input sentences or documents
    languages = docsLanguage
    # "en"(English, default)|"de"(German)|"es"(Spanish)|"fr"(French)|"ja"(Japanese)
  )

}, error = function(err) {

  # Print error
  geterrmessage()

})
```

## Credits

All Microsoft Cognitive Services components are Copyright © Microsoft.

For great introductions to the underlying REST API, please refer to [this](https://azure.microsoft.com/en-us/documentation/articles/cognitive-services-text-analytics-quick-start/)
and [that](https://blogs.technet.microsoft.com/machinelearning/2015/04/08/introducing-text-analytics-in-the-azure-ml-marketplace/) link.

## Meta

This package is certainly functional. It's also the first time it is available
on CRAN. Therefore, if you observe unexpected behaviors (a.k.a. bugs), please be
kind enough to submit a bug report on GitHub (not via email) with a minimal
reproducible example [here](https://github.com/philferriere/mscstexta4r/issues).

License: MIT + [file](./LICENSE)

To retrieve `{mscstexta4r}` citation information, run `citation(package = 'mscstexta4r')`

This project is released with a [Contributor Code of Conduct](./CONDUCT.md). By
 participating in this project, you agree to abide by its terms.

## About the Author

For more info about the author of this R package, please visit:

[![https://www.linkedin.com/in/philferriere](https://dl.dropboxusercontent.com/u/5888080/LinkedInDevLead.png)](https://www.linkedin.com/in/philferriere)

### 2016-06-13 R/textaDetectLanguages.R

@@ -1,0 +1,143 @@
+
+#' @title Detects the languages used in documents.
+#'
+#' @description This function returns the language detected in a sentence or
+#' documents along with a confidence score between 0 and 1. A scores equal to 1
+#' indicates 100% certainty. A total of 120 languages are supported.
+#'
+#' Internally, this function invokes the Microsoft Cognitive Services Text
+#' Analytics REST API documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#'
+#' You MUST have a valid Microsoft Cognitive Services account and an API key for
+#' this function to work properly. See \url{https://www.microsoft.com/cognitive-services/en-us/pricing}
+#' for details.
+#'
+#' @export
+#'
+#' @param documents (character vector) Vector of sentences or documents on
+#' which to perform language detection.
+#'
+#' @param numberOfLanguagesToDetect (integer) Number of languages to detect. Set
+#' to 1 by default. Use a higher value if individual documents contain a mix of
+#' languages.
+#'
+#' @return An S3 object of the class \code{\link{texta}}. The results are stored
+#' in the \code{results} dataframe inside this object. The dataframe contains
+#' the original sentences or documents, the name of the detected language, the
+#' ISO 639-1 code of the detected language, and a confidence score. If an error
+#' occurred during processing, the dataframe will also have an \code{error}
+#' column that describes the error.
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+#'
+#' @examples \dontrun{
+#'
+#'  docsText <- c(
+#'    "The Louvre or the Louvre Museum is the world's largest museum.",
+#'    "Le musee du Louvre est un musee d'art et d'antiquites situe au centre de Paris.",
+#'    "El Museo del Louvre es el museo nacional de Francia.",
+#'    "Il Museo del Louvre a Parigi, in Francia, e uno dei piu celebri musei del mondo.",
+#'    "Der Louvre ist ein Museum in Paris."
+#'  )
+#'
+#'  tryCatch({
+#'
+#'    # Detect languages used in documents
+#'    docsLanguage <- textaDetectLanguages(
+#'      documents = docsText,           # Input sentences or documents
[…]

### 2016-06-13 R/textaDetectTopics.R

@@ -1,0 +1,285 @@
+
+#' @title Detects the top topics in a group of text documents.
+#'
+#' @description This function returns the top detected topics for a list of
+#' submitted text documents. A topic is identified with a key phrase, which can
+#' be one or more related words. At least 100 text documents must be submitted,
+#' however this API is designed to detect topics across hundreds to thousands of
+#' documents. For best performance, limit each document to a short, human
+#' written text paragraph such as review, conversation or user feedback.
+#'
+#' You can provide a list of stop words to control which words or documents are
+#' filtered out. You can also supply a list of topics to exclude from the
+#' response. Finally, you can also provide min/max word frequency count
+#' thresholds to exclude rare/ubiquitous document topics.
+#'
+#' We recommend using the \code{\link{textaDetectTopics}} function in synchronous
+#' mode, in which case it will return only after topic detection has completed.
+#' If you decide to call this function in asynchronous mode, you will need to
+#' call the \code{\link{textaDetectTopicsStatus}} function periodically yourself
+#' until the Microsoft Cognitive Services server complete topic detection and
+#' results become available.
+#'
+#' \strong{IMPORTANT NOTE: If you're calling \code{\link{textaDetectTopics}} in
+#' synchronous mode within the R console REPL (interactive mode), it will
+#' appear as if the console has hanged. This is \emph{EXPECTED}. The function
+#' hasn't crashed. It is simply in "sleep mode", activating itself periodically
+#' and then going back to sleep, until the results have become available. In
+#' sleep mode, even though it appears "stuck", \code{\link{textaDetectTopics}}
+#' dodesn't use any CPU resources. While the function is operating in sleep
+#' mode, you \emph{WILL NOT} be able to use the console until the function
+#' completes. If need to operate the console while topic detection is being
+#' performed by the Microsoft Cognitive services servers, you should call
+#' \code{\link{textaDetectTopics}} in asynchronous mode and then call
+#' \code{\link{textaDetectTopicsStatus}} yourself repeteadly afterwards, until
+#' results are available.}
+#'
+#' Note that one transaction is charged per text document submitted.
+#'
[…]

### 2016-06-13 R/textaDetectTopicsStatus.R

@@ -1,0 +1,162 @@
+
+#' @title Retrieves the status of an topic detection operation submitted for
+#' processing.
+#'
+#' @description This function retrieves the status of an asynchronous topic
+#' detection operation previously submitted for processing. If the the operation
+#' has reached a 'Succeeded' state, this function will also return the results.
+#'
+#' Internally, this function invokes the Microsoft Cognitive Services Text
+#' Analytics REST API documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#'
+#' You MUST have a valid Microsoft Cognitive Services account and an API key for
+#' this function to work properly. See \url{https://www.microsoft.com/cognitive-services/en-us/pricing}
+#' for details.
+#'
+#' @export
+#'
+#' @param operation (textatopics) textatopics S3 object returned by the original
+#' call to \code{\link{textaDetectTopics}}.
+#'
+#' @return An S3 object of the class \code{\link{textatopics}} with the results
+#' of the topic detection operation. See \code{\link{textatopics}} for details.
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+#'
+#' @examples \dontrun{
+#'  load("./data/yelpChineseRestaurantReviews.rda")
+#'  set.seed(1234)
+#'  documents <- sample(yelpChReviews$text, 1000)
+#'
+#'  tryCatch({
+#'
+#'    # Start async topic detection
+#'    operation <- textaDetectTopics(
+#'      documents,                  # At least 100 docs/sentences
+#'      stopWords = NULL,           # Stop word list (optional)
+#'      topicsToExclude = NULL,     # Topics to exclude (optional)
+#'      minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
+#'      maxDocumentsPerWord = NULL, # Threshold to exclude ubiquitous topics (optional)
+#'      resultsPollInterval = 0L    # Poll interval (in s, default: 20s, use 0L for async)
+#'    )
+#'
+#'    # Poll the servers until the work completes or until we time out
+#'    resultsPollInterval <- 60L
+#'    resultsTimeout <- 1200L
+#'    startTime <- Sys.time()
+#'    endTime <- startTime + resultsTimeout
+#'
+#'    while (Sys.time() <= endTime) {
+#'      sleepTime <- startTime + resultsPollInterval - Sys.time()
+#'      if (sleepTime > 0)
[…]

### 2016-06-13 R/textaHttr.R

@@ -1,0 +1,71 @@
+
+## @title Uses the \code{httr} package to send an HTTP request.
+##
+## @param verb (character) HTTP verb ("GET" or "POST").
+##
+## @param method (character) Action method to add to the REST API base URL.
+##
+## @param query (character) Query params to follow the method (optional).
+##
+## @param query (character) HTTP request body (optional).
+##
+## @return An S3 object of the class \code{response}.
+##
+## @author Phil Ferriere \email{pferriere@hotmail.com}
+
+textaHttr <- function(verb, method, query = NULL, body = NULL) {
+
+  VERB <- getExportedValue("httr", verb)
+  apikeyHeader <- httr::add_headers("Ocp-Apim-Subscription-Key" = textaGetKey())
+  res.request <- paste0(textaGetURL(), method)
+
+  if (is.null(body) || length(body) == 0) {
+
+    res <- VERB(
+      res.request,
+      httr::content_type_json(),
+      apikeyHeader,
+      query = query
+    )
+
+  } else {
+
+    res <- VERB(
+      res.request,
+      body = body,
+      apikeyHeader,
+      query = query
+    )
+
+  }
+
+  # Note: The topic detection API returns 202 to signal it's
+  # processing the request, so don't fail the call in that case
+  if (res$status_code > 202) {
+
+    # Try to extract a formatted error message
+    obj <- try({err <- jsonlite::fromJSON(httr::content(res, "text", encoding = "UTF-8"))$error}, silent = TRUE)
+
+    if (class(obj) != "try-error" && !is.null(err)) {
+
+      # We could extract a formatted error message
+      if (err$code == "Unspecified")
+        err$code <- res$status_code
+      list(statusCode = err$code, errorMessage = err$message)
+
+      stop(sprintf("mscstexta4r: %s - %s", err$code, err$message), call. = FALSE)
+
+    } else {
+
+      # We couldn't extract a formatted error message
+      err <- httr::http_condition(res, "error")
+      errmsg <- httr::content(res, "text", encoding = "UTF-8")
+      list(statusCode = err$message, errorMessage = errmsg)
+
+      stop(sprintf("mscstexta4r: %s - %s", err$message, errmsg), call. = FALSE)
+    }
+
+  }
+
+  res
+}

### 2016-06-13 R/textaInit.R

@@ -1,0 +1,236 @@
+
+#' @title Initializes the \pkg{mscstexta4r} package.
+#'
+#' @description This function initializes the Microsoft Cognitive Services
+#' Text Analytics REST API key and URL by reading them either from a
+#' configuration file or environment variables.
+#'
+#' This function \strong{MUST} be called right after package load and before calling
+#' any \pkg{mscstexta4r} core functions, or these functions will fail.
+#'
+#' The \code{\link{textaInit}} configuration function will first check to see
+#' if the variable \code{MSCS_TEXTANALYTICS_CONFIG_FILE} exists in the system
+#' environment. If it does, the package will use that as the path to the
+#' configuration file.
+#'
+#' If \code{MSCS_TEXTANALYTICS_CONFIG_FILE} doesn't exist, it will look for
+#' the file \code{.mscskeys.json} in the current user's home directory (that's
+#' \code{~/.mscskeys.json} on Linux, and something like \code{C:/Users/Phil/Documents/.mscskeys.json}
+#' on Windows). If the file is found, the package will load the API key and URL
+#' from it.
+#'
+#' If using a file, please make sure it has the following structure:
+#'
+#' \preformatted{
+#' {
+#'   "textanalyticsurl": "https://westus.api.cognitive.microsoft.com/texta/analytics/v2.0/",
+#'   "textanalyticskey": "...MSCS Text Analytics API key goes here..."
+#' }
+#' }
+#'
+#' If no configuration file is found, \code{\link{textaInit}} will attempt to
+#' pick up its configuration information from two Sys env variables instead:
+#'
+#' \code{MSCS_TEXTANALYTICS_URL} - the URL for the Text Analytics REST API.
+#'
+#' \code{MSCS_TEXTANALYTICS_KEY} -  your personal Text Analytics REST API key.
+#'
+#' \code{\link{textaInit}} needs to be called \emph{only once}, after package
+#' load.
+#'
+#' @export
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+#'
+#' @examples \dontrun{
+#'  textaInit()
+#' }
+textaInit <- function() {
+
+  # Get config info from file
+  configFile <- textaGetConfigFile()
+
+  if (file.exists(configFile)) {
+
+    texta <- jsonlite::fromJSON(configFile)
+
+    if (is.null(texta[["textanalyticskey"]])) {
+      assign("texta", NULL, envir = .textapkgenv)
[…]

### 2016-06-13 R/textaKeyPhrases.R

@@ -1,0 +1,159 @@
+
+#' @title Returns the key talking points in sentences or documents.
+#'
+#' @description This function returns the the key talking points in a list of
+#' sentences or documents. The following languages are currently supported:
+#' English, German, Spanish and Japanese.
+#'
+#' Internally, this function invokes the Microsoft Cognitive Services Text
+#' Analytics REST API documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#'
+#' You MUST have a valid Microsoft Cognitive Services account and an API key for
+#' this function to work properly. See \url{https://www.microsoft.com/cognitive-services/en-us/pricing}
+#' for details.
+#'
+#' @export
+#'
+#' @param documents (character vector) Vector of sentences or documents for
+#' which to extract key talking points.
+#'
+#' @param languages (character vector) Languages of the sentences or documents,
+#' supported values: "en"(English, default), "de"(German), "es"(Spanish),
+#' "fr"(French), "ja"(Japanese)
+#'
+#' @return An S3 object of the class \code{\link{texta}}. The results are stored
+#' in the \code{results} dataframe inside this object. The dataframe contains
+#' the original sentences or documents and their key talking points. If an error
+#' occurred during processing, the dataframe will also have an \code{error}
+#' column that describes the error.
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+#'
+#' @examples \dontrun{
+#'
+#'  docsText <- c(
+#'    "Loved the food, service and atmosphere! We'll definitely be back.",
+#'    "Very good food, reasonable prices, excellent service.",
+#'    "It was a great restaurant.",
+#'    "If steak is what you want, this is the place.",
+#'    "The atmosphere is pretty bad but the food is quite good.",
+#'    "The food is quite good but the atmosphere is pretty bad.",
+#'    "I'm not sure I would come back to this restaurant.",
+#'    "The food wasn't very good.",
+#'    "While the food was good the service was a disappointment.",
+#'    "I was very disappointed with both the service and my entree."
+#'  )
+#'  docsLanguage <- rep("en", length(docsText))
+#'
+#'  tryCatch({
+#'
+#'    # Get key talking points in documents
[…]

### 2016-06-13 R/textaObject.R

@@ -1,0 +1,48 @@
+
+#' @title The \code{texta} object
+#'
+#' @description The \code{texta} object exposes formatted results, the REST API JSON
+#' response, and the HTTP request:
+#'
+#' \itemize{
+#'   \item \code{result} the results in \code{data.frame} format
+#'   \item \code{json} the REST API JSON response
+#'   \item \code{request} the HTTP request
+#' }
+#'
+#' @name texta
+#'
+#' @family texta methods
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+NULL
+
+texta <- function(results = NULL, json = NULL, request = NULL) {
+
+  # Validate input params
+  if (!is.null(results))
+    stopifnot(is.data.frame(results))
+  if (!is.null(json))
+    stopifnot(is.character(json), length(json) == 1)
+  if (!is.null(request))
+    stopifnot(class(request) == "request")
+
+  # Return results as S3 object of class "texta"
+  structure(list(results = results, json = json, request = request), class = "texta")
+}
+
+is.texta <- function(x) {
+  inherits(x, "texta")
+}
+
+#' @export
+print.texta <- function(x, ...) {
+
+  cat("texta [", x$request$url, "]\n", sep = "")
+  aintNoVT100NoMo <- panderOptions("table.split.table")
+  panderOptions("table.split.table", getOption("width"))
+  pandoc.table(x$results)
+  panderOptions("table.split.table", aintNoVT100NoMo)
+
+}
+

### 2016-06-13 R/textaPackage.R

@@ -1,0 +1,160 @@
+
+#' @title R Client for the Microsoft Cognitive Services Text Analytics REST API
+#'
+#' @description \pkg{mscstexta4r} is a client/wrapper/interface for the Microsoft
+#' Cognitive Services (MSCS) Text Analytics (Text Analytics) REST API. To use this
+#' package, you MUST have a valid account with \url{https://www.microsoft.com/cognitive-services}.
+#' Once you have an account, Microsoft will provide you with a (free) API key
+#' you can use with this package.
+#'
+#' @section Package Loading and Configuration:
+#'
+#' After loading the \pkg{mscstexta4r} package with the \code{library()} function,
+#' you must call the \code{\link{textaInit}} before you can call any of
+#' the core \pkg{mscstexta4r} functions.
+#'
+#' The \code{\link{textaInit}} configuration function will first check to see
+#' if the variable \code{MSCS_TEXTANALYTICS_CONFIG_FILE} exists in the system
+#' environment. If it does, the package will use that as the path to the
+#' configuration file.
+#'
+#' If \code{MSCS_TEXTANALYTICS_CONFIG_FILE} doesn't exist, it will look for
+#' the file \code{.mscskeys.json} in the current user's home directory (that's
+#' \code{~/.mscskeys.json} on Linux, and something like \code{C:/Users/Phil/Documents/.mscskeys.json}
+#' on Windows). If the file is found, the package will load the API key and URL
+#' from it.
+#'
+#' If using a file, please make sure it has the following structure:
+#'
+#' \preformatted{
+#' {
+#'   "textanalyticsurl": "https://westus.api.cognitive.microsoft.com/texta/analytics/v2.0/",
+#'   "textanalyticskey": "...MSCS Text Analytics API key goes here..."
+#' }
+#' }
+#'
+#' If no configuration file is found, \code{\link{textaInit}} will attempt to
+#' pick up its configuration information from two Sys env variables instead:
+#'
+#' \code{MSCS_TEXTANALYTICS_URL} - the URL for the Text Analytics REST API.
+#'
+#' \code{MSCS_TEXTANALYTICS_KEY} -  your personal Text Analytics REST API key.
+#'
+#' @section The MSCS Text Analytics REST API:
+#'
+#' Microsoft Cognitive Services -- formerly known as Project Oxford -- are a set
+#' of APIs, SDKs and services that developers can use to add AI features to
+#' their apps. Those features include emotion and video detection; facial,
[…]

### 2016-06-13 R/textaSentiment.R

@@ -1,0 +1,164 @@
+
+#' @title Assesses the sentiment of sentences or documents.
+#'
+#' @description This function returns a numeric score between 0 and 1 with
+#' scores close to 1 indicating positive sentiment and scores close to 0
+#' indicating negative sentiment.
+#'
+#' Sentiment score is generated using classification techniques. The input
+#' features of the classifier include n-grams, features generated from
+#' part-of-speech tags, and word embeddings. English, French, Spanish and
+#' Portuguese text are supported.
+#'
+#' Internally, this function invokes the Microsoft Cognitive Services Text
+#' Analytics REST API documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#'
+#' You MUST have a valid Microsoft Cognitive Services account and an API key for
+#' this function to work properly. See \url{https://www.microsoft.com/cognitive-services/en-us/pricing}
+#' for details.
+#'
+#' @export
+#'
+#' @param documents (character vector) Vector of sentences or documents for
+#' which to assess sentiment.
+#'
+#' @param languages (character vector) Languages of the sentences or documents,
+#' supported values: "en"(English, default), "es"(Spanish), "fr"(French),
+#' "pt"(Portuguese)
+#'
+#' @return An S3 object of the class \code{\link{texta}}. The results are stored
+#' in the \code{results} dataframe inside this object. The dataframe contains
+#' the original sentences or documents and their sentiment score. If an error
+#' occurred during processing, the dataframe will also have an \code{error}
+#' column that describes the error.
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+#'
+#' @examples \dontrun{
+#'
+#'  docsText <- c(
+#'    "Loved the food, service and atmosphere! We'll definitely be back.",
+#'    "Very good food, reasonable prices, excellent service.",
+#'    "It was a great restaurant.",
+#'    "If steak is what you want, this is the place.",
+#'    "The atmosphere is pretty bad but the food is quite good.",
+#'    "The food is quite good but the atmosphere is pretty bad.",
+#'    "I'm not sure I would come back to this restaurant.",
+#'    "The food wasn't very good.",
[…]

### 2016-06-13 R/textatopicsObject.R

@@ -1,0 +1,103 @@
+
+#' @title The \code{textatopics} object
+#'
+#' @description The \code{textatopics} object exposes formatted results for the
+#' \code{\link{textaDetectTopics}} API, this REST API's JSON response, and the
+#' HTTP request:
+#'
+#' \itemize{
+#'   \item \code{status} the operation's current status ("NotStarted"|"Running"|"Succeeded")
+#'   \item \code{documents} a \code{data.frame} with the documents and a unique
+#'   string ID for each
+#'   \item \code{topics} a \code{data.frame} with the identified topics, a
+#'   unique string ID for each, and a prevalence score for each topic (count of
+#'   documents assigned to topic)
+#'   \item \code{topicAssignments} a \code{data.frame} with all the topics
+#'   (identified by their topic ID) assigned to each document (identified by
+#'   their document ID), and a distance score for each topic assignment (between
+#'   0 and 1; the lower the distance score the stronger the topic affiliation)
+#'   \item \code{json} the REST API JSON response
+#'   \item \code{request} the HTTP request
+#' }
+#'
+#' @name textatopics
+#'
+#' @family textatopics methods
+#'
+#' @author Phil Ferriere \email{pferriere@hotmail.com}
+NULL
+
+textatopics <- function(
+  status = NULL,
+  operationId = NULL,
+  operationType = NULL,
+  documents = NULL,
+  topics = NULL,
+  topicAssignments = NULL,
+  json = NULL,
+  originalRequest = NULL,
+  request = NULL
+  ) {
+
+  # Validate input params
+  if (!is.null(status))
+    stopifnot(is.character(status), length(status) == 1)
+  if (!is.null(operationId))
+    stopifnot(is.character(operationId), length(operationId) == 1)
+  if (!is.null(operationType))
+    stopifnot(is.character(operationType), length(operationType) == 1)
+  if (!is.null(documents))
+    stopifnot(is.data.frame(documents))
+  if (!is.null(topics))
+    stopifnot(is.data.frame(topics))
+  if (!is.null(topicAssignments))
+    stopifnot(is.data.frame(topicAssignments))
+  if (!is.null(json))
+    stopifnot(is.character(json), length(json) == 1)
+  if (!is.null(originalRequest))
+    stopifnot(class(originalRequest) == "request")
+  if (!is.null(request))
+    stopifnot(class(request) == "request")
+
[…]

### 2016-06-13 R/zzz.R

@@ -1,0 +1,2 @@
+
+.textapkgenv <- new.env(parent = emptyenv())

### 2016-06-13 tests/testthat.R

@@ -1,0 +1,12 @@
+# testthat testing instructions are at http://r-pkgs.had.co.nz/tests.html
+# quick notes:
+#   put all your tests in tests/testthat folder
+#   each test file should start with test and end in .R
+#   since we use secret API keys, don't run the tests on CRAN
+
+library("testthat")
+
+if (identical(tolower(Sys.getenv("NOT_CRAN")), "true")) {
+  library("mscstexta4r")
+  test_check("mscstexta4r")
+}

### 2016-06-13 tests/testthat/testDetectLanguages.R

@@ -1,0 +1,88 @@
+context("testDetectLanguages")
+
+if (!("package:mscstexta4r" %in% search())) {
+  library("mscstexta4r")
+  textaInit()
+} else {
+  textaInit()
+}
+
+docsText <- c(
+  "The Louvre or the Louvre Museum is the world's largest museum.",
+  "Le musée du Louvre est un musée d'art et d'antiquités situé au centre de Paris.",
+  "El Museo del Louvre es el museo nacional de Francia.",
+  "Il Museo del Louvre a Parigi, in Francia, è uno dei più celebri musei del mondo.",
+  "Der Louvre ist ein Museum in Paris."
+)
+docsText2 <- c(
+  "",
+  "Le musée du Louvre est un musée d'art et d'antiquités situé au centre de Paris.",
+  "El Museo del Louvre es el museo nacional de Francia.",
+  "Il Museo del Louvre a Parigi, in Francia, è uno dei più celebri musei del mondo.",
+  "Der Louvre ist ein Museum in Paris."
+)
+
+test_that("textaDetectLanguages returns expected result structure", {
+
+  skip_on_cran()
+
+  res <- textaDetectLanguages(docsText)
+
+  expect_that(res, is_a("texta"))
+  expect_that(length(res), equals(3))
+  expect_that(res[["request"]], is_a("request"))
+  expect_that(res[["json"]], is_a("character"))
+  expect_that(res[["results"]], is_a("data.frame"))
+  expect_that(nrow(res[["results"]]), equals(5))
+  expect_that(ncol(res[["results"]]), equals(4))
+  expect_that(names(res[["results"]])[1], equals("text"))
+  expect_that(names(res[["results"]])[2], equals("name"))
+  expect_that(names(res[["results"]])[3], equals("iso6391Name"))
+  expect_that(names(res[["results"]])[4], equals("score"))
+
+  # documents: one document is empty, other params: good,
+  # expect overall success but results to still have an error column
+  # note that this is how it is currently handled by the underlying REST API
+  # and is not consistent with the way it is handled by the Sentiment REST API
+  res <- textaDetectLanguages(docsText2)
+
+  expect_that(res, is_a("texta"))
+  expect_that(length(res), equals(3))
+  expect_that(res[["request"]], is_a("request"))
+  expect_that(res[["json"]], is_a("character"))
+  expect_that(res[["results"]], is_a("data.frame"))
[…]

### 2016-06-13 tests/testthat/testDetectTopics.R

@@ -1,0 +1,216 @@
+context("testDetectTopics")
+
+# Load yelpChReviews100 text reviews
+load("./data/yelpChineseRestaurantReviews100.rda")
+
+test_that("textaDetectTopics returns expected result structure", {
+
+  skip_on_cran()
+
+  res <- textaDetectTopics(
+    documents = yelpChReviews100, # At least 100 documents
+    stopWords = NULL,             # Stop word list (optional)
+    topicsToExclude = NULL,       # Topics to exclude (optional)
+    minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
+    maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
+    resultsPollInterval = 30L,    # Poll interval (in s, default: 30s, use 0L for async)
+    resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
+    verbose = FALSE               # If set to TRUE, print every poll status to stdout
+  )
+
+  # Expected results
+  # topics (first 10):
+  # -------------------
+  #  keyPhrase   score
+  # ----------- -------
+  #    soup       19
+  #    beef       10
+  #    curry       8
+  #     egg        7
+  #   flavor       7
+  #    pork        7
+  #    China       6
+  #    roll        6
+  #   people       5
+  #   review       5
+
+  expect_that(res, is_a("textatopics"))
+  expect_that(length(res), equals(9))
+  expect_that(res[["status"]], is_a("character"))
+  expect_that(res[["status"]], equals("Succeeded"))
+  expect_that(res[["operationId"]], is_a("character"))
+  expect_that(res[["operationType"]], is_a("character"))
+  expect_that(res[["operationType"]], equals("topics"))
+  expect_that(res[["originalRequest"]], is_a("request"))
+  expect_that(res[["request"]], is_a("request"))
+  expect_that(res[["json"]], is_a("character"))
+  expect_that(res[["documents"]], is_a("data.frame"))
+  expect_that(names(res[["documents"]])[1], equals("id"))
+  expect_that(names(res[["documents"]])[2], equals("text"))
+  expect_that(res[["topics"]], is_a("data.frame"))
+  expect_that(names(res[["topics"]])[1], equals("id"))
+  expect_that(names(res[["topics"]])[2], equals("score"))
+  expect_that(names(res[["topics"]])[3], equals("keyPhrase"))
[…]

### 2016-06-13 tests/testthat/testKeyPhrases.R

@@ -1,0 +1,77 @@
+context("testKeyPhrases")
+
+docsText <- c(
+  "Loved the food, service and atmosphere! We'll definitely be back.",
+  "Very good food, reasonable prices, excellent service.",
+  "It was a great restaurant.",
+  "If steak is what you want, this is the place.",
+  "The atmosphere is pretty bad but the food is quite good.",
+  "The food is quite good but the atmosphere is pretty bad.",
+  "I'm not sure I would come back to this restaurant.",
+  "The food wasn't very good.",
+  "While the food was good the service was a disappointment.",
+  "I was very disappointed with both the service and my entree."
+)
+docsText2 <- c(
+  "",
+  "Very good food, reasonable prices, excellent service.",
+  "It was a great restaurant.",
+  "If steak is what you want, this is the place.",
+  "The atmosphere is pretty bad but the food is quite good.",
+  "The food is quite good but the atmosphere is pretty bad.",
+  "I'm not sure I would come back to this restaurant.",
+  "The food wasn't very good.",
+  "While the food was good the service was a disappointment.",
+  "I was very disappointed with both the service and my entree."
+)
+docsLanguage <- rep("en", length(docsText))
+
+test_that("textaKeyPhrases returns expected result structure", {
+
+  skip_on_cran()
+
+  res <- textaKeyPhrases(docsText, docsLanguage)
+
+  expect_that(res, is_a("texta"))
+  expect_that(length(res), equals(3))
+  expect_that(res[["request"]], is_a("request"))
+  expect_that(res[["json"]], is_a("character"))
+  expect_that(res[["results"]], is_a("data.frame"))
+  expect_that(nrow(res[["results"]]), equals(10))
+  expect_that(ncol(res[["results"]]), equals(2))
+  expect_that(names(res[["results"]])[1], equals("text"))
+  expect_that(names(res[["results"]])[2], equals("keyPhrases"))
+})
+
+test_that("textaKeyPhrases fails with an error", {
+
+  skip_on_cran()
+
+  # documents: bad, other params: good, expect error
+  expect_that(textaKeyPhrases(documents = 0), throws_error())
+
+  # languages: bad, other params: good, expect error
+  expect_that(textaKeyPhrases(docsText, languages = 0), throws_error())
+
+  # documents: one document is empty, other params: good,
[…]

### 2016-06-13 tests/testthat/testSentiment.R

@@ -1,0 +1,78 @@
+context("testSentiment")
+
+docsText <- c(
+  "Loved the food, service and atmosphere! We'll definitely be back.",
+  "Very good food, reasonable prices, excellent service.",
+  "It was a great restaurant.",
+  "If steak is what you want, this is the place.",
+  "The atmosphere is pretty bad but the food is quite good.",
+  "The food is quite good but the atmosphere is pretty bad.",
+  "I'm not sure I would come back to this restaurant.",
+  "The food wasn't very good.",
+  "While the food was good the service was a disappointment.",
+  "I was very disappointed with both the service and my entree."
+)
+docsText2 <- c(
+  "",
+  "Very good food, reasonable prices, excellent service.",
+  "It was a great restaurant.",
+  "If steak is what you want, this is the place.",
+  "The atmosphere is pretty bad but the food is quite good.",
+  "The food is quite good but the atmosphere is pretty bad.",
+  "I'm not sure I would come back to this restaurant.",
+  "The food wasn't very good.",
+  "While the food was good the service was a disappointment.",
+  "I was very disappointed with both the service and my entree."
+)
+docsLanguage <- rep("en", length(docsText))
+
+test_that("textaSentiment returns expected result structure", {
+
+  skip_on_cran()
+
+  res <- textaSentiment(docsText, docsLanguage)
+
+  expect_that(res, is_a("texta"))
+  expect_that(length(res), equals(3))
+  expect_that(res[["request"]], is_a("request"))
+  expect_that(res[["json"]], is_a("character"))
+  expect_that(res[["results"]], is_a("data.frame"))
+  expect_that(nrow(res[["results"]]), equals(10))
+  expect_that(ncol(res[["results"]]), equals(2))
+  expect_that(names(res[["results"]])[1], equals("text"))
+  expect_that(names(res[["results"]])[2], equals("score"))
+
+})
+
+test_that("textaSentiment fails with an error", {
+
+  skip_on_cran()
+
+  # documents: bad, other params: good, expect error
+  expect_that(textaSentiment(documents = 0), throws_error())
+
+  # languages: bad, other params: good, expect error
+  expect_that(textaSentiment(docsText, languages = 0), throws_error())
+
+  # documents: one document is empty, other params: good,
+  # note that throwing an error is how it's handled by the underlying sentiment REST API
[…]

### 2016-06-14 R/textaDetectTopics.R
Run tests and vignette in verbose mode

@@ -261,10 +261,7 @@ textaDetectTopics <- function(
       startTime <- Sys.time()
 
       # Poll for results
-      results <- textaDetectTopicsStatus(operation)
-      if (verbose == TRUE) {
-        cat(sprintf("[operationId: %s, status: %s]\n", operationId, results$status))
-      }
+      results <- textaDetectTopicsStatus(operation, verbose)
       if (results$status != "NotStarted" && results$status != "Running")
         break;
     }
@@ -275,10 +272,7 @@ textaDetectTopics <- function(
 
   } else {
     # Poll just once and return
-    results <- textaDetectTopicsStatus(operation)
-    if (verbose == TRUE) {
-      cat(sprintf("[operationId: %s, status: %s]\n", operationId, results$status))
-    }
+    results <- textaDetectTopicsStatus(operation, verbose)
   }
 
   results

### 2016-06-14 R/textaDetectTopicsStatus.R

@@ -18,6 +18,8 @@
 #' @param operation (textatopics) textatopics S3 object returned by the original
 #' call to \code{\link{textaDetectTopics}}.
 #'
+#' @param verbose (logical) If set to TRUE, print poll status to stdout.
+#'
 #' @return An S3 object of the class \code{\link{textatopics}} with the results
 #' of the topic detection operation. See \code{\link{textatopics}} for details.
 #'
@@ -37,7 +39,7 @@
 #'      topicsToExclude = NULL,     # Topics to exclude (optional)
 #'      minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
 #'      maxDocumentsPerWord = NULL, # Threshold to exclude ubiquitous topics (optional)
-#'      resultsPollInterval = 0L    # Poll interval (in s, default: 20s, use 0L for async)
+#'      resultsPollInterval = 0L    # Poll interval (in s, default: 30s, use 0L for async)
 #'    )
 #'
 #'    # Poll the servers until the work completes or until we time out
@@ -116,11 +118,13 @@
 #' }
 
 textaDetectTopicsStatus <- function(
-  operation  # An S3 object of class "textatopics"
+  operation,       # An S3 object of class "textatopics"
+  verbose = FALSE  # If set to TRUE, print poll status to stdout
 ) {
 
-  # Validate input param
+  # Validate input params
   stopifnot(is.textatopics(operation))
+  stopifnot(is.logical(verbose))
 
   # Call the MSCS Text Analytics REST API
   res <- textaHttr(
@@ -145,6 +149,9 @@ textaDetectTopicsStatus <- function(
         }
       }
     }
+  }
+  if (verbose == TRUE) {
+    cat(sprintf("[operationId: %s, status: %s]\n", operation$operationId, status))
   }
 
   # Return results as S3 object of class "textatopics"

### 2016-06-14 tests/testthat/testDetectTopics.R

@@ -13,9 +13,9 @@ test_that("textaDetectTopics returns expected result structure", {
     topicsToExclude = NULL,       # Topics to exclude (optional)
     minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
     maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
-    resultsPollInterval = 30L,    # Poll interval (in s, default: 30s, use 0L for async)
+    resultsPollInterval = 60L,    # Poll interval (in s, default: 30s, use 0L for async)
     resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
-    verbose = FALSE               # If set to TRUE, print every poll status to stdout
+    verbose = TRUE                # If set to TRUE, print every poll status to stdout
   )
 
   # Expected results
@@ -82,9 +82,9 @@ test_that("textaDetectTopics topic control works correctly", {
     topicsToExclude = topicsToExclude,       # Topics to exclude (optional)
     minDocumentsPerWord = minDocumentsPerWord,   # Threshold to exclude rare topics (optional)
     maxDocumentsPerWord = maxDocumentsPerWord,   # Threshold to exclude ubiquitous topics (optional)
-    resultsPollInterval = 20L,    # Poll interval (in s, default: 20s, use 0L for async)
+    resultsPollInterval = 60L,    # Poll interval (in s, default: 30s, use 0L for async)
     resultsTimeout = 600L,        # Give up timeout (in s, default: 600s = 10mn)
-    verbose = FALSE                # If set to TRUE, print every poll status to stdout
+    verbose = TRUE                # If set to TRUE, print every poll status to stdout
   )
 
   expect_that(res, is_a("textatopics"))
@@ -141,9 +141,9 @@ shortStopWordList = c(
     topicsToExclude = NULL,       # Topics to exclude (optional)
     minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
     maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
-    resultsPollInterval = 30L,    # Poll interval (in s, default: 20s, use 0L for async)
+    resultsPollInterval = 60L,    # Poll interval (in s, default: 30s, use 0L for async)
     resultsTimeout = 1200L,       # Give up timeout (in s, default: 600s = 10mn)
-    verbose = FALSE               # If set to TRUE, print every poll status to stdout
[…]

### 2016-06-14 README.Rmd
Remove build shields Combine textaDetectTopics tests

@@
 ```
-[![Build Status](https://api.travis-ci.org/philferriere/mscstexta4r.png)](https://travis-ci.org/philferriere/mscstexta4r)
-[![codecov.io](https://codecov.io/github/philferriere/mscstexta4r/coverage.svg?branch=master)](https://codecov.io/github/philferriere/mscstexta4r?branch=master)
-[![CRAN Version](http://www.r-pkg.org/badges/version/mscstexta4r)](https://cran.r-project.org/package=mscstexta4r)
 

### 2016-06-14 tests/testthat/testDetectTopics.R

@@ -7,119 +7,42 @@ test_that("textaDetectTopics returns expected result structure", {
 
   skip_on_cran()
 
-  res <- textaDetectTopics(
-    documents = yelpChReviews100, # At least 100 documents
-    stopWords = NULL,             # Stop word list (optional)
-    topicsToExclude = NULL,       # Topics to exclude (optional)
-    minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
-    maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
-    resultsPollInterval = 60L,    # Poll interval (in s, default: 30s, use 0L for async)
-    resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
-    verbose = TRUE                # If set to TRUE, print every poll status to stdout
+  shortStopWordList = c(
+    "I", "a", "about", "an", "are", "as", "at", "be", "by", "com", "for", "from", "how", "in", "is", "it",
+    "of", "on", "or", "that", "the", "this", "to", "was", "what", "when", "where", "who", "will", "with", "www"
   )
-
-  # Expected results
-  # topics (first 10):
-  # -------------------
-  #  keyPhrase   score
-  # ----------- -------
-  #    soup       19
-  #    beef       10
-  #    curry       8
-  #     egg        7
-  #   flavor       7
-  #    pork        7
-  #    China       6
-  #    roll        6
-  #   people       5
-  #   review       5
-
-  expect_that(res, is_a("textatopics"))
-  expect_that(length(res), equals(9))
-  expect_that(res[["status"]], is_a("character"))
-  expect_that(res[["status"]], equals("Succeeded"))
-  expect_that(res[["operationId"]], is_a("character"))
-  expect_that(res[["operationType"]], is_a("character"))
-  expect_that(res[["operationType"]], equals("topics"))
-  expect_that(res[["originalRequest"]], is_a("request"))
-  expect_that(res[["request"]], is_a("request"))
-  expect_that(res[["json"]], is_a("character"))
-  expect_that(res[["documents"]], is_a("data.frame"))
-  expect_that(names(res[["documents"]])[1], equals("id"))
-  expect_that(names(res[["documents"]])[2], equals("text"))
-  expect_that(res[["topics"]], is_a("data.frame"))
-  expect_that(names(res[["topics"]])[1], equals("id"))
[…]

### 2016-06-14 README.Rmd
Restore build shields

@@
 ```
+[![Build Status](https://api.travis-ci.org/philferriere/mscstexta4r.png)](https://travis-ci.org/philferriere/mscstexta4r)
+[![codecov.io](https://codecov.io/github/philferriere/mscstexta4r/coverage.svg?branch=master)](https://codecov.io/github/philferriere/mscstexta4r?branch=master)
 

### 2016-06-15 README.Rmd
Documentation update

--- 2016-06-13 README.Rmd
@@
 is a suite of text analytics web services built with Azure Machine Learning that
-can be used to analyze unstructured text. The API supports four text analysis
-operations:
+can be used to analyze unstructured text. The API supports the following text
+analysis operations:
 
@@
 operating in sleep mode, you *WILL NOT* be able to use the console before the
-function completes. If you need to operate the console while topic detection is
-being performed by the Microsoft Cognitive services servers, you should call
-`textaDetectTopics()` in asynchronous mode and then call
-`textaDetectTopicsStatus()` yourself repeatedly afterwards, until results are
-available.
+function completes.
+
+If you need to operate the console while topic detection is being performed by
+the Microsoft Cognitive services servers, you should call `textaDetectTopics()`
+in asynchronous mode and then call `textaDetectTopicsStatus()` yourself
+repeatedly afterwards, until results are available.
 
@@
 
+## Related Microsoft Cognitive Services Packages
+
+`{mscsweblm4r}`, a R Client for the Microsoft Cognitive Services **Web Language
+Model** REST API, is also available on [CRAN](https://cran.r-project.org/package=mscsweblm4r)
+
 ## Meta
 
-This package is certainly functional. It's also the first time it is available
-on CRAN. Therefore, if you observe unexpected behaviors (a.k.a. bugs), please be
-kind enough to submit a bug report on GitHub (not via email) with a minimal
-reproducible example [here](https://github.com/philferriere/mscstexta4r/issues).
+Please report any issues or bugs [here](https://github.com/philferriere/mscstexta4r/issues).
 

### 2016-06-15 R/textaDetectTopicsStatus.R

@@ -1,9 +1,9 @@
 
-#' @title Retrieves the status of an topic detection operation submitted for
+#' @title Retrieves the status of a topic detection operation submitted for
 #' processing.
 #'
 #' @description This function retrieves the status of an asynchronous topic
-#' detection operation previously submitted for processing. If the the operation
+#' detection operation previously submitted for processing. If the operation
 #' has reached a 'Succeeded' state, this function will also return the results.
 #'
 #' Internally, this function invokes the Microsoft Cognitive Services Text

### 2016-06-15 R/textaPackage.R

@@ -7,6 +7,41 @@
 #' Once you have an account, Microsoft will provide you with a (free) API key
 #' you can use with this package.
 #'
+#' @section The MSCS Text Analytics REST API:
+#'
+#' Microsoft Cognitive Services -- formerly known as Project Oxford -- are a set
+#' of APIs, SDKs and services that developers can use to add AI features to
+#' their apps. Those features include emotion and video detection; facial,
+#' speech and vision recognition; and speech and language understanding.
+#'
+#' The Text Analytics REST API provides tools for natural language
+#' processing and is documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#
+#' The MSCS Text Analytics REST API supports the following text analytics operations:
+#'
+#' \itemize{
+#'  \item Sentiment analysis - Is a sentence or document generally positive or negative?
+#'  \item Topic detection - What's being discussed across a list of documents/reviews/articles?
+#'  \item Language detection - What language is a document written in?
+#'  \item Key talking points extraction - What's being discussed in a single document?
+#' }
+#'
+#' @section \pkg{mscstexta4r} Functions:
+#'
+#' The following \pkg{mscstexta4r} core functions are used to wrap the
+#' MSCS Text Analytics REST API:
+#'
+#' \itemize{
+#'  \item Sentiment analysis - \code{\link{textaSentiment}} function
+#'  \item Topic detection - \code{\link{textaDetectTopics}} and \code{\link{textaDetectTopicsStatus}} functions
+#'  \item Language detection - \code{\link{textaDetectLanguages}} function
+#'  \item Extraction of key talking points - \code{\link{textaKeyPhrases}} function
+#' }
+#'
+#' The \code{\link{textaInit}} configuration function is used to set the REST
+#' API URL and the private API key. It needs to be called \emph{only once},
+#' after package load, or the core functions will not work properly.
+#'
 #' @section Package Loading and Configuration:
 #'
 #' After loading the \pkg{mscstexta4r} package with the \code{library()} function,
@@ -39,41 +74,6 @@
 #' \code{MSCS_TEXTANALYTICS_URL} - the URL for the Text Analytics REST API.
 #'
 #' \code{MSCS_TEXTANALYTICS_KEY} -  your personal Text Analytics REST API key.
-#'
-#' @section The MSCS Text Analytics REST API:
-#'
-#' Microsoft Cognitive Services -- formerly known as Project Oxford -- are a set
[…]

### 2016-06-15 R/textaDetectLanguages.R
Bump document unique IDs from 5 to 8 chars

@@ -108,7 +108,7 @@ textaDetectLanguages <- function(
 
   # Combine documents in df easy to JSON encode in request body
   textaDF <- data.frame(
-    id = stringi::stri_rand_strings(length(documents), 5),
+    id = stringi::stri_rand_strings(length(documents), 8),
     text = documents,
     stringsAsFactors = FALSE
   )

### 2016-06-15 R/textaDetectTopics.R

@@ -204,7 +204,7 @@ textaDetectTopics <- function(
 
   # Combine documents in df easy to JSON encode in request body
   textaDF <- data.frame(
-    id = stringi::stri_rand_strings(length(documents), 5),
+    id = stringi::stri_rand_strings(length(documents), 8),
     text = documents,
     stringsAsFactors = FALSE
   )

### 2016-06-15 R/textaKeyPhrases.R

@@ -125,7 +125,7 @@ textaKeyPhrases <- function(
   # Combine documents in df easy to JSON encode in request body
   textaDF <- data.frame(
     language = languages,
-    id = stringi::stri_rand_strings(length(documents), 5),
+    id = stringi::stri_rand_strings(length(documents), 8),
     text = documents,
     stringsAsFactors = FALSE
   )

### 2016-06-15 R/textaSentiment.R

@@ -130,7 +130,7 @@ textaSentiment <- function(
   # Combine documents in df easy to JSON encode in request body
   textaDF <- data.frame(
     language = languages,
-    id = stringi::stri_rand_strings(length(documents), 5),
+    id = stringi::stri_rand_strings(length(documents), 8),
     text = documents,
     stringsAsFactors = FALSE
   )

### 2016-06-16 README.Rmd
Documentation refresh

@@
 features to their apps. Those features include emotion and video detection;
-facial, speech and vision recognition; and speech and natural language
-processing ([NLP](https://en.wikipedia.org/wiki/Natural_language_processing)).
+facial, speech and vision recognition; as well as speech and [NLP](https://en.wikipedia.org/wiki/Natural_language_processing).
 
@@
 is a suite of text analytics web services built with Azure Machine Learning that
-can be used to analyze unstructured text. The API supports the following text
-analysis operations:
+can be used to analyze unstructured text. The API supports the following
+operations:
 
@@
 
+## Package Installation
+
 To use the `{mscstexta4r}` R package, you **MUST** have a valid [account](https://www.microsoft.com/cognitive-services/en-us/pricing)
 with Microsoft Cognitive Services. Once you have an account, Microsoft will
-provide you with an [API key](https://en.wikipedia.org/wiki/Application_programming_interface_key).
-This key will be listed under your subscriptions.
+provide you with an [API key](https://en.wikipedia.org/wiki/Application_programming_interface_key)
+listed under your subscriptions. After you've configured `{mscstexta4r}` with
+your API key, you will be able to call the Text Analytics REST API from R, up
+to your maximum number of transactions per month and per minute.
 
-After you've configured `{mscstexta4r}` with your API key, you will be able to
-call the Text Analytics REST API from R, up to your maximum number of
-transactions per month and per minute.
-
-## Package Installation
-
-You can either install the latest **stable** version from CRAN:
+You can install the latest **stable** version of `{mscstexta4r}` from CRAN as
+follows:
 
@@
 
-Or, you can install the **development** version
+You can also install the **development** version using `{devtools}`:
 
@@
 
-```{r}
+```{r eval = FALSE}
 # Load yelpChReviews100 text reviews
@@
 })
+# Same results as in synchronous mode
 ```

### 2016-06-16 R/textaPackage.R

@@ -12,12 +12,11 @@
 #' Microsoft Cognitive Services -- formerly known as Project Oxford -- are a set
 #' of APIs, SDKs and services that developers can use to add AI features to
 #' their apps. Those features include emotion and video detection; facial,
-#' speech and vision recognition; and speech and language understanding.
+#' speech and vision recognition; as well as speech and NLP.
 #'
-#' The Text Analytics REST API provides tools for natural language
-#' processing and is documented at \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
-#
-#' The MSCS Text Analytics REST API supports the following text analytics operations:
+#' The Text Analytics REST API provides tools for NLP and is documented at
+#' \url{https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation}.
+#' This API supports the following operations:
 #'
 #' \itemize{
 #'  \item Sentiment analysis - Is a sentence or document generally positive or negative?
@@ -41,6 +40,16 @@
 #' The \code{\link{textaInit}} configuration function is used to set the REST
 #' API URL and the private API key. It needs to be called \emph{only once},
 #' after package load, or the core functions will not work properly.
+#'
+#' @section Prerequisites:
+#'
+#' To use the \pkg{mscstexta4r} R package, you \strong{MUST} have a valid
+#' account with Microsoft Cognitive Services (see \url{https://www.microsoft.com/cognitive-services/en-us/pricing}
+#' for details). Once you have an account, Microsoft will provide you with an
+#' API key listed under your subscriptions. After you've configured
+#' \pkg{mscstexta4r} with your API key (as explained in the next section), you
+#' will be able to call the Text Analytics REST API from R, up to your
+#' maximum number of transactions per month and per minute.
 #'
 #' @section Package Loading and Configuration:
 #'
@@ -77,8 +86,8 @@
 #'
 #' @section Synchronous vs Asynchronous Execution:
 #'
-#' All but \strong{one} core text analytics functions execute exclusively in
-#' synchronous mode. \code{\link{textaDetectTopics}} is the only function that
+#' All but \strong{ONE} core text analytics functions execute exclusively in
+#' synchronous mode: \code{\link{textaDetectTopics}} is the only function that
 #' can be executed either synchronously or asynchronously. Why? Because topic
 #' detection is typically a "batch" operation meant to be performed on thousands
 #' of related documents (product reviews, research articles, etc.).

### 2016-06-20 README.Rmd
Replace characters with accents in sample inputs

@@
   "The Louvre or the Louvre Museum is the world's largest museum.",
-  "Le musée du Louvre est un musée d'art et d'antiquités situé au centre de Paris.",
+  "Le musee du Louvre est un musee d'art et d'antiquites situe au centre de Paris.",
   "El Museo del Louvre es el museo nacional de Francia.",
-  "Il Museo del Louvre a Parigi, in Francia, è uno dei più celebri musei del mondo.",
+  "Il Museo del Louvre a Parigi, in Francia, e uno dei piu celebri musei del mondo.",
   "Der Louvre ist ein Museum in Paris."
@@
 
-All Microsoft Cognitive Services components are Copyright © Microsoft.
+All Microsoft Cognitive Services components are Copyright (c) Microsoft.
 

### 2016-06-21 R/textaDetectTopics.R
Documented English-only topic detection, made auto-print more robust, bumped version to 0.1.2

@@ -8,6 +8,8 @@
 #' documents. For best performance, limit each document to a short, human
 #' written text paragraph such as review, conversation or user feedback.
 #'
+#' English is the only language supported at this time.
+#'
 #' You can provide a list of stop words to control which words or documents are
 #' filtered out. You can also supply a list of topics to exclude from the
 #' response. Finally, you can also provide min/max word frequency count
@@ -47,7 +49,7 @@
 #'
 #' @param documents (character vector) Vector of sentences or documents on
 #' which to perform topic detection. At least 100 text documents must be
-#' submitted.
+#' submitted. English is the only language supported at this time.
 #'
 #' @param stopWords (character vector) Vector of stop words to ignore while
 #' performing topic detection (optional)
@@ -104,7 +106,7 @@
 #'
 #'    # Detect top topics in group of documents
 #'    topics <- textaDetectTopics(
-#'      documents,                  # At least 100 documents
+#'      documents,                  # At least 100 documents (English only)
 #'      stopWords = NULL,           # Stop word list (optional)
 #'      topicsToExclude = NULL,     # Topics to exclude (optional)
 #'      minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
@@ -172,7 +174,7 @@
 #' }
 
 textaDetectTopics <- function(
-  documents,                  # At least 100 documents
+  documents,                  # At least 100 documents (English only)
   stopWords = NULL,           # Stop word list (optional)
   topicsToExclude = NULL,     # Topics to exclude (optional)
   minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)

### 2016-06-21 R/textatopicsObject.R

@@ -6,7 +6,7 @@
 #' HTTP request:
 #'
 #' \itemize{
-#'   \item \code{status} the operation's current status ("NotStarted"|"Running"|"Succeeded")
+#'   \item \code{status} the operation's current status ("NotStarted"|"Running"|"Succeeded"|"Failed")
 #'   \item \code{documents} a \code{data.frame} with the documents and a unique
 #'   string ID for each
 #'   \item \code{topics} a \code{data.frame} with the identified topics, a
@@ -87,17 +87,20 @@ print.textatopics <- function(x, ...) {
   cat("status: ", x$status, "\n", sep = "")
   cat("operationId: ", x$operationId, "\n", sep = "")
   cat("operationType: ", x$operationType, "\n", sep = "")
-  aintNoVT100NoMo <- panderOptions("table.split.table")
-  panderOptions("table.split.table", getOption("width"))
-  if (exists("topics", where = x)) {
-    if (nrow(x$topics) > 20)
-      cat("topics (first 20):\n", sep = "")
-    else
-      cat("topics:\n", sep = "")
-    firstTopics <- utils::head(x$topics[with(x$topics, order(-score)),c(3,2)], 20)
-    row.names(firstTopics) <- NULL
-    pandoc.table(firstTopics)
+  if (x$status == "Succeeded") {
+    if (exists("topics", where = x)) {
+      if (!is.null(x$topics)) {
+        aintNoVT100NoMo <- panderOptions("table.split.table")
+        panderOptions("table.split.table", getOption("width"))
+        if (nrow(x$topics) > 20)
+          cat("topics (first 20):\n", sep = "")
+        else
+          cat("topics:\n", sep = "")
+        firstTopics <- utils::head(x$topics[with(x$topics, order(-score)),c(3,2)], 20)
+        row.names(firstTopics) <- NULL
+        pandoc.table(firstTopics)
+        panderOptions("table.split.table", aintNoVT100NoMo)
+      }
+    }
   }
-  panderOptions("table.split.table", aintNoVT100NoMo)
-
 }

### 2016-06-21 README.Rmd
Document that topic detection is English only

@@
 work well for short, human-written text such as reviews and user feedback.
+English is the only language supported at this time.
 
@@
 textaDetectTopics(
-  documents,                  # At least 100 documents
+  documents,                  # At least 100 documents (English only)
   stopWords = NULL,           # Stop word list (optional)
@@
   textaDetectTopics(
-    documents = yelpChReviews100, # At least 100 docs/sentences
+    documents = yelpChReviews100, # At least 100 docs/sentences (English only)
     stopWords = NULL,             # Stop word list (optional)
@@
   operation <- textaDetectTopics(
-    documents = yelpChReviews100, # At least 100 docs/sentences
+    documents = yelpChReviews100, # At least 100 docs/sentences (English only)
     resultsPollInterval = 0L      # Poll interval (in s, default: 30s, use 0L for async)

### 2016-06-22 R/textaObject.R
Make auto-print more robust

@@ -38,11 +38,24 @@ is.texta <- function(x) {
 #' @export
 print.texta <- function(x, ...) {
 
-  cat("texta [", x$request$url, "]\n", sep = "")
-  aintNoVT100NoMo <- panderOptions("table.split.table")
-  panderOptions("table.split.table", getOption("width"))
-  pandoc.table(x$results)
-  panderOptions("table.split.table", aintNoVT100NoMo)
+  if (exists("request", where = x)) {
+    if (!is.null(x$request)) {
+      if (exists("url", where = x$request)) {
+        if (!is.null(x$request$url)) {
+          cat("texta [", x$request$url, "]\n", sep = "")
+        }
+      }
+    }
+  }
+
+  if (exists("results", where = x)) {
+    if (!is.null(x$results)) {
+      aintNoVT100NoMo <- panderOptions("table.split.table")
+      panderOptions("table.split.table", getOption("width"))
+      pandoc.table(x$results)
+      panderOptions("table.split.table", aintNoVT100NoMo)
+    }
+  }
 
 }
 

### 2016-06-22 R/textatopicsObject.R

@@ -83,10 +83,34 @@ is.textatopics <- function(x) {
 #' @export
 print.textatopics <- function(x, ...) {
 
-  cat("textatopics [", x$originalRequest$url, "]\n", sep = "")
-  cat("status: ", x$status, "\n", sep = "")
-  cat("operationId: ", x$operationId, "\n", sep = "")
-  cat("operationType: ", x$operationType, "\n", sep = "")
+  if (exists("originalRequest", where = x)) {
+    if (!is.null(x$originalRequest)) {
+      if (exists("url", where = x$originalRequest)) {
+        if (!is.null(x$originalRequest$url)) {
+          cat("textatopics [", x$originalRequest$url, "]\n", sep = "")
+        }
+      }
+    }
+  }
+
+  if (exists("status", where = x)) {
+    if (!is.null(x$status)) {
+      cat("status: ", x$status, "\n", sep = "")
+    }
+  }
+
+  if (exists("operationId", where = x)) {
+    if (!is.null(x$operationId)) {
+      cat("operationId: ", x$operationId, "\n", sep = "")
+    }
+  }
+
+  if (exists("operationType", where = x)) {
+    if (!is.null(x$operationType)) {
+      cat("operationType: ", x$operationType, "\n", sep = "")
+    }
+  }
+
   if (x$status == "Succeeded") {
     if (exists("topics", where = x)) {
       if (!is.null(x$topics)) {
